### 2012-05-11 inst/examples/value_of_information.Rmd
value of information

 Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
 Compute the optimal solution under different forms of uncertainty and compare the results.

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.0     # noise in stock assessment measurement
sigma_i <- 0.0     # noise in implementation of the quota
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
````
Find the transition matrix

@@

``` {r }
sims_g <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

``` {r }
sigma_m <- 0.15     # noise in stock assessment measurement
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
````

@@

``` {r }
sims_gm <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

``` {r }
sigma_i <- 0.15     # noise in implementation of the quota
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
````

@@

``` {r }
sims_gmi <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

>>>>

 Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
 Compute the optimal solution under different forms of uncertainty.  The true uncertainty is much smaller than that assumed, just a small uncertainty in growth.  We compare the case where the uncertainty is equal to this tiny growth uncertainty to policies derived under much greater uncertainty assumptions, and see how the resulting profit varies.

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
````
Find the transition matrix

@@

Simulate.  The real world doesn't have as much uncertainty as we do in our knowledge of the state.

``` {r }
sigma_g <- 0.05    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
sims_g <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, profit=profit)
})
````

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.15     # noise in stock assessment measurement
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() 1
````

@@

``` {r }
sigma_g <- 0.05    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1
z_i <- function() 1
sims_gm <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.15     # noise in stock assessment measurement
sigma_i <- 0.15     # noise in implementation of the quota
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
````

@@

``` {r }
sigma_g <- 0.05    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1
z_i <- function() 1
sims_gmi <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````
